Workshop Instructions: Reproducible Scientific Manuscripts

### 2024-05-16 Instructions.qmd
Update Instructions.qmd

>>>>

In this part of the workshop, you will integrate all of the skills, you acquired in the previous lessons.
You will firstly execute a self-contained minimal example that is provided in this repository.
Secondly, you will recreate the minimal example using all the components provided in the folder "02_practice".
Thirdly, you will create your own first reproducible manuscript based on a conventional manuscript you already have.
And finally, you can use the checklist provided in the "03_supplement" folder to go over your project and see how many reproducibility measure you applied.

<!-- Please insert links to the appropriate workshop components and folders -->
